Algebraic File Synchronization: Adequacy and Completeness

### 2018-07-04 p2/comparisons.tex
Improved introduction
Updated notation

\section{Related Work}

@@

The former observation is supported by Berzan and Ramsey, who in \cite{CBNR} 
describe different general reconciliation policies.
The liberal (maximal) policy propagates all updates to all replicas where
the update does not break the filesystem, while a conservative policy
refrains from updating any node that is below a node with conflicting commands.
They show that the reconciliation algorithm in \cite{NREC} implements
an intermediate policy as one can easily construct two- or three-replica scenarios
where an update could clearly be propagated, but it is excluded.
To rephrase the example in \cite{CBNR}, consider the following two
update sequences that have been applied to replicas $\FS_A$ and $\FS_B$:
\begin{align*}
A&=\caaa{\empt}{\valdi}{\nn}\cc\caaa{\empt}{\valf}{n} \\
B&=\caaa{\empt}{\valdii}{\nn}
\end{align*}
where $\parent(n)=\nn$ (\cite{NREC} did not require all directories to have the same value).
Clearly $\caaa{\empt}{\valf}{n}$ could be applied to $\FS_B$, but it is not as
it must be preceded by creating the directory, which conflicts with the same command in $B$
due to the different value.
(Introducing a third replica which has not changed at all further complicates the picture.)
The current algorithm no longer needs to specify that there can be no conflicts
on preceding commands, and, to use the above terminology, implements a fully liberal policy.

@@

As a test of the proposed reconciliation algorithm, 
we compare our definition of conflicting
updates to how conflicts are defined by Balasubramaniam and Pierce
in their state-based approach implemented in the Unison synchronizer \cite{BP}.
As we noted in \cite{NREC}, the update detector they describe provides a safe estimate of nodes
(paths) at which updates occurred.
It marks some nodes as \emph{dirty} in a way that we know that at non-dirty nodes
the filesystems (replicas) have not changed between their common original state and current state
(see Definition 3.1.1 in \cite{BP}).
The \emph{dirty} marks are also up-closed, that is, all ancestor nodes of a dirty node
are also dirty (Fact 3.1.3 in \cite{BP}).
And finally, in our notation, 
a conflict is detected between replicas $\FS_A$ and $\FS_B$ at node $n$
if $n$ is marked as dirty in both $\FS_A$ and $\FS_B$, and
$\FS_A(n)\neq\FS_B(n)$, and $n$ does not point to a directory in both replicas.
(In other words, 
$\FS_A(n)\not\in\setd \vee \FS_B(n)\not\in\setd$; see section 4.1 in \cite{BP}.
Let us note that there is an alternative approach to defining an algorithm for
the same synchronizer by Pierce and Vouillon in \cite{PV}.)

It can be easily seen that due to an edge case, 
not all conflicts detected based on the above definition
entails a conflict based on our system; that is, \cite{BP} describes a more
conservative policy.
We use the example we described in \cite{NREC},
where $\nn=\parent(n)$ and $\FS(\nn)$ is a directory and $\FS(n)$ is a file, and
the two replicas are derived in the following way:
\begin{gather*}
\FS_A = \cfba{n} \cc \cdba{\nn} \aFS \\
\FS_B = \cfba{n} \aFS.
\end{gather*}
Then, $\nn$ is dirty in both replicas:
in $\FS_A$ it was modified, and in $\FS_B$ one of its descendants was modified.
Moreover, $\FS_A(\nn)\neq\FS_B(\nn)$ and $\FS_A(\nn)=\empt\not\in\setd$,
and therefore a conflict is detected at $\nn$.
(This behaviour is preserved in the more recent Harmony synchronizer.
See ``delete/delete conflicts'' in \cite{PSG,FGKPS}.)
Our reconciliation algorithm detects no conflicts;
instead, it propagates $\cdba{\nn}$ to $\FS_B$, which we think is as expected
and desired.

@@

Now we only need to show that $\FS_A(n)\neq\FS_B(n)$, because from this 
and $|\setd|=1$ we will also
know that at least one of these values is not a directory,
and therefore there is a conflict at $n$ in the state-based reconciler.
If $n=m$, this follows from the fact that $\cxynv\neq\czwmv$ 
(because they are not in $A\cap B$),
as from \cref{worksinputmatch} we have $X=Z$,
and therefore the above can only be true
if $\FS_A(n)=\valvy\neq\valvw=\FS_B(n)$.
If $n\descendant m$ and there is no command on $n$ in $B$, then it is also
true as $\cxynv$ is not an assertion command, and therefore 
$\FS_A(n)\neq\FS(n)=\FS_B(n)$, where $\FS$ is the common ancestor of the replicas.
Finally, if there is a command on $n$ in $B$, then 
from $\cxynv\in A\setminus B$ we know
it must be different from $\cxynv$, and similarly to the first case,
we have $\FS_A(n)\neq\FS_B(n)$.
\end{proof}

>>>>

\section{Related Work}\mlabel{sec_relatedwork}

@@

The former observation is supported by Berzan and Ramsey, who in \cite{CBNR} 
describe different general reconciliation policies.
The liberal (maximal) policy propagates all updates to all replicas where
the update does not break the filesystem, while a conservative policy
refrains from updating any node that is below a node with conflicting commands.
They show that the reconciliation algorithm in \cite{NREC} implements
an intermediate policy as one can easily construct two- or three-replica scenarios
where an update could clearly be propagated, but it is excluded.
To rephrase the example in \cite{CBNR}, consider the following two
update sequences that have been applied to replicas $\FS_A$ and $\FS_B$:
\begin{align*}
A&=\caaa{\empt}{\valdi}{\pn}\cc\caaa{\empt}{\valf}{n} \\
B&=\caaa{\empt}{\valdii}{\pn}
\end{align*}
(\cite{NREC} did not require all directories to have the same value).
Clearly $\caaa{\empt}{\valf}{n}$ could be applied to $\FS_B$, but it is not as
it must be preceded by creating the directory, which conflicts with the same command in $B$
due to the different value.
(Introducing a third replica which has not changed at all further complicates the picture.)
The current algorithm no longer needs to specify that there can be no conflicts
on preceding commands, and, to use the above terminology, implements a fully liberal policy.

@@

As a test of the proposed reconciliation algorithm, 
we compare our definition of conflicting
updates to how conflicts are defined by Balasubramaniam and Pierce
in their state-based approach implemented in the Unison synchronizer \cite{BP}.
As we noted in \cite{NREC}, the update detector they describe provides a safe estimate of nodes
(paths) at which updates occurred.
It marks some nodes as \emph{dirty} in a way that we know that at non-dirty nodes
the filesystems (replicas) have not changed between their common original state and current state
(see Definition 3.1.1 in \cite{BP}).
The \emph{dirty} marks are also up-closed, that is, all ancestor nodes of a dirty node
are also dirty (Fact 3.1.3 in \cite{BP}).
And finally, in our notation, 
a conflict is detected between replicas $\FS_A$ and $\FS_B$ at node $n$
if $n$ is marked as dirty in both $\FS_A$ and $\FS_B$, and
$\FS_A(n)\neq\FS_B(n)$, and $n$ does not point to a directory in both replicas.
(In other words, 
$[\FS_A(n)]\neq[\vald]$ or $[\FS_B(n)]\neq[\vald]$; see section 4.1 in \cite{BP}.
Let us note that there is an alternative approach to defining an algorithm for
the same synchronizer by Pierce and Vouillon in \cite{PV}.)

It can be easily seen that due to an edge case, 
not all conflicts detected based on the above definition
entails a conflict based on our system; that is, \cite{BP} describes a more
conservative policy.
We use the example we described in \cite{NREC},
where $\FS(\pn)$ is a directory and $\FS(n)$ is a file, and
the two replicas are derived in the following way:
\begin{gather*}
\FS_A = (\cfba{n} \cc \cdba{\pn}) \aFS \\
\FS_B = \cfba{n} \aFS.
\end{gather*}
Then, $\pn$ is dirty in both replicas:
in $\FS_A$ it was modified, and in $\FS_B$ one of its descendants was modified.
Moreover, $\FS_A(\pn)\neq\FS_B(\pn)$ and $[\FS_A(\pn)]\neq[\vald]$ as it is empty.
Therefore, a conflict is detected at $\pn$.
(This behaviour is preserved in the more recent Harmony synchronizer.
See ``delete/delete conflicts'' in \cite{PSG,FGKPS}.)
Our reconciliation algorithm detects no conflicts;
instead, it propagates $\cdba{\pn}$ to $\FS_B$, which we think is as expected
and desired.

@@

Now we only need to show that $\FS_A(n)\neq\FS_B(n)$, because from this 
and $|\setd|=1$ we will also
know that at least one of these values is not a directory,
and therefore there is a conflict at $n$ in the state-based reconciler.

If $n=m$, this follows from the fact that $\cxynv\neq\czwmv$ 
(because they are not in $A\cap B$),
as from \cref{worksinputmatch} we have $[x]=[z]$,
and therefore necessarily $y\neq w$,
that is, $\FS_A(n)=y\neq w=\FS_B(n)$.

If $n\descendant m$ and there is no command on $n$ in $B$, then 
because $\cxynv$ is not an assertion command, we again have
$\FS_A(n)\neq\FS(n)=\FS_B(n)$, where $\FS$ is the common ancestor of the replicas.
Finally, if there is a command on $n$ in $B$, then 
from $\cxynv\in A\setminus B$ we know
it must be different from $\cxynv$, and similarly to the first case,
we have $\FS_A(n)\neq\FS_B(n)$.
\end{proof}
